---
title: "Tree Analisys"
author: "Ana Cecilia Montes & Ayra Reyla"
date: "2 october 2015"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

In this assisment, we analyse the characteristic of both Black Cherry Trees and Loblobly Pine Trees combining two different dataframes built-in  in R Studio. 

The first data frama cointans information about the growth of Loblolly trees. This species is a common pine specie in the Southern US. According to the data, loblolly pine tress has on average 32 fts (see Table 1). On the other hand, Prunus serotina, commonly called black cherry trees are also native in North America but they are on average two times bigger than Loblolly trees. Their hight on average is 76 fts (see Table 2).  

###Table 1.Loblolly trees summary Statistics 
```{r Loblolly, echo=FALSE}
summary(Loblolly$height)
```
###Table 2. Cherry trees summary Statistics 
```{r trees, echo=FALSE}
summary(trees$Height)
# Standard Deviation 
```
## Tree Height Distribution
A major diference between Loblolly and Cherry is the height distribution. While, Lobloly trees height can range from 3 to 70 fts, for Cherry trees the height ranges from 60 to 90 fts.

```{r pressure, echo=FALSE}
hist(Loblolly$height, 
     xlab = "Height (fts)", 
     main = "Histogram of Loblolly Pine Tree height")
hist(trees$Height, 
     xlab = "Height (ft)", 
     main = 'Height of Black Cherry Trees')
```

# Standard Deviation 
```{r pressure3, echo=FALSE}
#Loblolly Trees Standard Deviation 
sd(Loblolly$height)
#Black Cherry Trees Standard Deviation 
sd(trees$Height)
```