---
title: "Tree Analisys"
author: "Ana Cecilia Montes & Ayra Reyla"
date: "2 october 2015"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

In this assisment, we analyse the characteristic of both Black Cherry Trees and Loblobly Pine Trees combining two different dataframes built-in  in R Studio. 

  The first data frame cointans information about the growth of Loblolly trees. This specie is common in the Southern US. According to the data, loblolly pine tress has on average `r mean(Loblolly$height, na.rm = TRUE)` fts (see Table 1). On the other hand, Prunus serotina, commonly called black cherry trees are also native in North America but they are on average two times bigger than Loblolly trees. Their hight on average is `r mean(trees$Height, na.rm = TRUE) fts (see Table 2).  

###Table 1.Loblolly trees summary Statistics 
```{r Loblolly, echo=FALSE}
summary(Loblolly$height)
```
###Table 2. Cherry trees summary Statistics 
```{r trees, echo=FALSE}
summary(trees$Height)
```
## Tree Height Distribution
A major diference between Loblolly and Cherry is the height distribution. While, Lobloly trees height can range from 3 to 70 fts, for Cherry trees the height ranges from 60 to 90 fts. The variance of loblolly tree's height is `r var(Loblolly$height)` and a standard deviation of `r sd(Loblolly$height)`. On the other hand, The variance of Cherry tree's height is `r var(trees$Height)` and a standard deviation of `r sd(trees$Height)`

```{r pressure, echo=FALSE}
hist(Loblolly$height, 
     xlab = "Height (fts)", 
     main = "Histogram of Loblolly Pine Tree height")
hist(trees$Height, 
     xlab = "Height (ft)", 
     main = 'Height of Black Cherry Trees')
```
We observe that Black Cherry Trees' height follows a normal distribution. This is not the case for Loblolly trees height.

##Box Plots
Box plots or whisker plots graphically ilustrates the groups of numerical data through quartiles. The bottom and top of the box are always the first and third quartiles and the band inside the box is the second quartile or the median. 

```{r pressure4, echo=FALSE}
boxplot(trees$Height, main = "% of Cherry Tree Height Around the Median")
boxplot(Loblolly$height, main = "% of Loblolly Tree Height Around the Median")
boxplot(trees$Girth, main = "% of Tree Girth Around the Median")
boxplot(trees$Volume, main = "% of Tree Volume Around the Median")
```

## Girth Distribution
Another variable of interest is 

```{r pressure3, echo=FALSE}
hist(trees$Girth, 
     xlab = "Girth (In)", 
     main = 'Girth of Black Cherry Trees')
```
